Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Start on explanation of results

>>>>

    \subsection{Ground state energies for two-dimensional quantum dots}
        Here we show the ground state energies for the two-dimensional quantum
        dots using restriced Hartree-Fock (RHF), coupled cluster doubles using
        both the harmonic oscillator basis and the Hartree-Fock basis which we
        construct after running the RHF-method. We have chosen the convergence
        criteria to be $\num{1e-6}$ in our results for the sake of comparison
        with M. P. Lohne\cite{lohne2011ab}.
